\documentclass[a4paper,10pt]{article}

\usepackage{parskip}
\usepackage{hologo}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.92, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{5pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Use Helvetica
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

% non-numbered pages
\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{\textbf{SHIVAM GOVIND RAO}} \\[6pt]
\normalsize{\href{mailto:ishivamgovindrao@gmail.com}{ishivamgovindrao@gmail.com} $|$ +91-6386220277 $|$ \href{https://www.shivamgovindrao.com}{www.shivamgovindrao.com}} \\
\normalsize{\href{https://github.com/BLAZE7SHADOW}{github.com/BLAZE7SHADOW} $|$ \href{https://www.linkedin.com/in/shivam-govind-rao-138881157/}{linkedin.com/in/shivam-govind-rao-138881157} $|$ Gurugram, India}
\end{tabularx}

\vspace{3pt}

\section{SUMMARY}

Frontend engineer with 2.5+ years building production React applications end-to-end --- component architecture, state management, responsive UI, and service-layer integration. Comfortable owning a feature from customer requirement through implementation, testing, code review, and documentation. Strong clean-code discipline (DRY/KISS refactors, class-based service design, unit/integration testing) and hands-on experience debugging cross-browser and cross-platform rendering issues in production.

\section{EXPERIENCE}

\textbf{Software Development Engineer} \hfill \textit{Jan 2025 -- April 2026}\\
\textbf{Diagna AI (FAXFlo)} $|$ Gurugram, India \hfill \textit{First Engineer $\cdot$ Full-Stack}

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    \textbf{UI ownership}: shipped the React 19 frontend solo --- \textbf{110+ components}, lazy-loaded routes, responsive layouts, and code-splitting that cut bundle size by $\sim$\textbf{60\%}; built a custom \textbf{Zustand + Immer} document-editing engine with field-level diff/patch updates and a high-resolution \textbf{PDF.js} viewer (300 DPI multi-page rendering).
    }

    \small{\item
    \textbf{Clean code \& OOP}: refactored duplicated path-manipulation logic into a shared utility layer (\texttt{PathOperations}, \texttt{EditValidation}, \texttt{ResultMergeService}), eliminating repetition across 3 files (DRY); encapsulated core services into class-based implementations (\texttt{BedrockService}, \texttt{UserConsentService}, \texttt{PatientService}) for testability and separation of concerns.
    }

    \small{\item
    \textbf{Testing \& documentation}: added a \textbf{Jest + Supertest} suite for API integration testing, and \textbf{Swagger/OpenAPI} documentation across 40+ REST endpoints, in line with coding guidelines and delivery quality norms.
    }

    \small{\item
    Built the production Node.js/Express/PostgreSQL backend consumed by the UI --- \textbf{40+ REST endpoints}, JWT/RBAC auth, input validation, and Redis-backed BullMQ queues --- and a \textbf{distributed AWS document pipeline} (S3 $\cdot$ SQS $\cdot$ Textract $\cdot$ SNS $\cdot$ Bedrock) processing \textbf{1,000+ documents daily} at 99\%+ uptime with dead-letter-queue handling and idempotency keys.
    }

    \small{\item
    Integrated \textbf{Claude (Sonnet), GPT-4o, and AWS Bedrock} for multi-model document classification at \textbf{$\sim$95\% accuracy across 40+ categories}, with custom prompting, confidence scoring, and retry logic for malformed model outputs.
    }

    \small{\item
    Built the \textbf{HIPAA-compliant PostHog analytics dashboard} and ran the investor + clinic demo that closed the \textbf{first paying US clinic}; regularly coordinated requirements and delivery timelines directly with stakeholders as the sole frontend/full-stack owner.
    }
\end{itemize}

\vspace{3pt}

\textbf{Frontend Developer} \hfill \textit{Dec 2023 -- Jan 2025}\\
\textbf{Oriserve (\href{https://voicegenie.ai/}{VoiceGenie.ai})} $|$ Noida, India

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    Sole frontend engineer --- grew \textbf{VoiceGenie from 0 to \$10K MRR in 11 months}; the responsive dashboard and marketing site I shipped directly closed the first enterprise customers.
    }

    \small{\item
    Built a \textbf{live variable composer} for AI voice scripts (drop \texttt{@name} / \texttt{@appointment} tokens that resolve per-contact at call time) and integrated \textbf{HubSpot CRM, ElevenLabs, GoHighLevel, and Cal.com} into a single workflow.
    }

    \small{\item
    Cut page load times \textbf{30--50\%} through code-splitting, lazy loading, and intelligent caching. \textbf{Stack:} React.js, Redux, TypeScript, Material UI, Netlify.
    }
\end{itemize}

\vspace{3pt}

\section{PROJECTS}

\textbf{MotionStudio} \hfill \href{https://motionstudio-six.vercel.app/}{Live} $|$ \href{https://github.com/BLAZE7SHADOW/MotionStudio}{GitHub}\\
\textit{Personal project, 2026}

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    Browser-based video editor (React 19, TypeScript strict, Zustand) built around a single-mutation-point architecture (one aggregate-root state object, immutable updates, structural-sharing undo/redo). Debugged and fixed several \textbf{cross-browser/rendering quirks} in production: a \texttt{contenteditable} cursor-reset bug caused by React re-rendering the DOM selection, browser autoplay-policy handling for muted video preview, and \texttt{blob:} URL incompatibility between browser preview and Node-based export. \textbf{Stack:} Remotion, React, TypeScript, Tailwind, Vite.
    }
\end{itemize}

\vspace{3pt}

\section{SKILLS}

\textbf{Languages:} JavaScript, TypeScript, Python, SQL, C/C++, HTML5, CSS3

\textbf{Frontend:} React 19, Next.js, Redux, Zustand, Tailwind CSS, Material UI, Ant Design, Responsive Web Design, Framer Motion, GSAP, Vite, PDF.js, React Router

\textbf{Engineering Practices:} OOP, Clean Code (DRY, KISS), Unit \& Integration Testing (Jest, Supertest), Cross-Browser Compatibility, Code Review, API Documentation (Swagger/OpenAPI), Secure Coding (JWT/RBAC)

\textbf{Backend:} Node.js, Express.js, PostgreSQL, Prisma, Redis, BullMQ

\textbf{Cloud \& Infra:} AWS (S3, SQS, SNS, Bedrock, Textract, EC2, Lambda), Docker, Git, CI/CD

\textbf{AI \& Automation:} Claude, GPT-4o, AWS Bedrock, Prompt Engineering, RPA (Robocorp, Playwright)

\vspace{3pt}

\section{EDUCATION}

\textbf{B.Tech in Computer Science \& Engineering} \hfill \textit{2019 - 2023}\\
IET, Dr. Ram Manohar Lohia Awadh University, Ayodhya \hfill \textit{81\%}

\end{document}
