\documentclass[a4paper,10pt]{article}

\usepackage{parskip}
\usepackage{hologo}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.92, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{5pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Use Helvetica
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

% non-numbered pages
\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{\textbf{SHIVAM GOVIND RAO}} \\[6pt]
\normalsize{\href{mailto:ishivamgovindrao@gmail.com}{ishivamgovindrao@gmail.com} $|$ +91-6386220277 $|$ \href{https://www.shivamgovindrao.com}{www.shivamgovindrao.com}} \\
\normalsize{\href{https://github.com/BLAZE7SHADOW}{github.com/BLAZE7SHADOW} $|$ \href{https://www.linkedin.com/in/shivam-govind-rao-138881157/}{linkedin.com/in/shivam-govind-rao-138881157} $|$ Gurugram, India}
\end{tabularx}

\vspace{3pt}

\section{SUMMARY}

Backend-focused engineer with 2.5+ years designing and operating production distributed systems --- async job queues, multi-model AI inference pipelines, and browser-automation integrations processing 1,000+ transactions daily at 99\%+ uptime. Owned services end-to-end: API design, queue architecture, failure recovery, and observability, as the sole backend engineer on the team, with working fluency in the React frontends those services power.

\section{EXPERIENCE}

\textbf{Software Development Engineer} \hfill \textit{Jan 2025 -- April 2026}\\
\textbf{Diagna AI (FAXFlo)} $|$ Gurugram, India \hfill \textit{First Engineer $\cdot$ Backend \& Systems Owner}

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    Architected a \textbf{distributed AWS document pipeline} (S3 $\cdot$ SQS $\cdot$ Textract $\cdot$ SNS $\cdot$ Bedrock) processing \textbf{1,000+ medical documents daily} at 99\%+ uptime, with a \textbf{dead-letter queue} and idempotency keys for exactly-once processing guarantees; designed a \textbf{scheduled auto-retry sweep} (every $\sim$5 hours) that re-drives stuck DLQ jobs automatically, so most transient failures self-heal without manual intervention.
    }

    \small{\item
    Built the production \textbf{Node.js/Express/PostgreSQL} backend --- \textbf{40+ REST endpoints}, JWT/RBAC auth, input validation, \textbf{Redis-backed BullMQ} queues, and Prisma ORM --- documented with \textbf{Swagger/OpenAPI} and covered by a \textbf{Jest + Supertest} integration-test suite.
    }

    \small{\item
    Integrated \textbf{Claude (Sonnet), GPT-4o, and AWS Bedrock} for multi-model document classification at \textbf{$\sim$95\% accuracy across 40+ categories}, extracting structured patient data with custom prompting, confidence scoring, and retry logic for malformed model outputs.
    }

    \small{\item
    Engineered a \textbf{Python RPA automation suite} (Robocorp $\cdot$ Playwright $\cdot$ FastAPI $\cdot$ Redis RQ) to write structured data into an EHR with no usable API --- OTP/2FA login, patient search with disambiguation, and document upload via a deeply nested iframe UI, treated as a systems-integration problem rather than a scripting one.
    }

    \small{\item
    Built an \textbf{AI SMS/Voice orchestration layer} (Twilio, Telnyx, Vonage, VAPI, ElevenLabs) for automated appointment scheduling and follow-up, cutting manual outreach by $\sim$\textbf{70\%}; instrumented a \textbf{HIPAA-compliant PostHog analytics dashboard} for pipeline and EMR-sync observability.
    }

    \small{\item
    Also shipped the \textbf{React 19 frontend} consuming these APIs (110+ components, $\sim$60\% bundle reduction) when the team had no dedicated frontend engineer --- full API-to-UI ownership when needed.
    }
\end{itemize}

\vspace{3pt}

\textbf{Frontend Developer} \hfill \textit{Dec 2023 -- Jan 2025}\\
\textbf{Oriserve (\href{https://voicegenie.ai/}{VoiceGenie.ai})} $|$ Noida, India

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    Sole frontend engineer --- grew \textbf{VoiceGenie from 0 to \$10K MRR in 11 months}; integrated \textbf{HubSpot CRM, ElevenLabs, GoHighLevel, and Cal.com} into a single workflow with a live per-contact variable-resolution system for AI voice scripts.
    }

    \small{\item
    Cut page load times \textbf{30--50\%} through code-splitting, lazy loading, and intelligent caching. \textbf{Stack:} React, Redux, TypeScript, Material UI, Netlify.
    }
\end{itemize}

\vspace{3pt}

\section{PROJECTS}

\textbf{MotionStudio} \hfill \href{https://motionstudio-six.vercel.app/}{Live} $|$ \href{https://github.com/BLAZE7SHADOW/MotionStudio}{GitHub}\\
\textit{Personal project, 2026}

\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \small{\item
    Browser-based video editor (Remotion, React 19, TypeScript strict). Designed around a \textbf{single-mutation-point / aggregate-root} state architecture --- one \texttt{Project} object owns all data, mutated through one function --- so undo/redo, autosave, and WYSIWYG preview fell out of the data model instead of being built per-feature. \textbf{Stack:} Remotion, React, TypeScript, Zustand, Vite.
    }
\end{itemize}

\vspace{3pt}

\section{SKILLS}

\textbf{Backend:} Node.js, Express.js, FastAPI, PostgreSQL, Prisma, Redis, BullMQ, JWT Auth, RBAC, Swagger/OpenAPI

\textbf{Cloud \& Infra:} AWS (S3, SQS, SNS, Bedrock, Textract, Lambda, EC2), Docker, CI/CD, Git

\textbf{Distributed Systems:} Async Job Queues, Dead-Letter Queues \& Retry Design, Idempotency, Rate Limiting, Observability (PostHog)

\textbf{AI \& Automation:} Claude, GPT-4o, AWS Bedrock, Prompt Engineering, RPA (Robocorp, Playwright), VAPI, ElevenLabs, Twilio

\textbf{Languages:} Python, TypeScript, JavaScript, SQL, C/C++

\textbf{Frontend:} React 19, Next.js, Redux, Zustand, Tailwind CSS, PDF.js

\vspace{3pt}

\section{EDUCATION}

\textbf{B.Tech in Computer Science \& Engineering} \hfill \textit{2019 - 2023}\\
IET, Dr. Ram Manohar Lohia Awadh University, Ayodhya \hfill \textit{81\%}

\end{document}
